NOSQL\\ BEST PRACTICES

### 2018-03-27 pgconfus2018/presentation.tex
More slides, diagrams and examples

@@

>>>>

        \begin{flushleft}
            PostgreSQL 11 have HOT updates for some expression indexes, which will
            eliminate this problem.
        \end{flushleft}

@@

        \begin{itemize}[label={\MVRightarrow}]
            \item There is no proper selectivity estimation for jsonb
            \item Optimizer can give wrong estimations for GIN and complex queries
            \item Functional indexes
        \end{itemize}

\fontsize{13pt}{14}\selectfont
\section{How much to write?}
\fontsize{17pt}{18}\selectfont

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Jsonb vs Json}

        \includegraphics[width=0.7\textwidth,center]{jsonb_header.png}

        \includegraphics[width=0.8\textwidth,center]{wal.png}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{How much to write?}

        \begin{itemize}[label={\MVRightarrow}]
            \item Every update leads to update of an entire document (but it's ok)
            \item WAL can have a full document or just a diff
            \item Old and new tuples fit into the same page - diff
            \item Old and new tuples fit into the same page - full
            \item If logical decoding is enabled - full
        \end{itemize}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{How much to write?}
